
The BYU DNA Sequencing Center (DNASC) provides state-of-the-art DNA sequencing services to internal and external 
users. An essential part of the provision of these services is the sharing and storage of files generated in the 
center.

The DNASC website \linklsdnasc{lsdnasc.byu.edu} will get three new pages, accessible 
through links in a dropdown listing called ``Data''. Each page will consist mainly of 
tabular data which will include links to popup windows with additional data and actions. 
The Users and Drives tables will be populated with data collected from frontend users. 
The data in the Movies table will be maintained by a backend. All data will be read in 
from and written to a database (i.e. a Globus ``\linkglobusindex{index}'') using the 
\linkglobussearch{Globus Search web API}. The frontend will also have functionality 
to initiate downloading, uploading, and sharing of files located on a storage system 
administered by BYU Office of Research Computing (ORC) via the \linkglobustransfer{Globus Transfer web API}.

In general, the new pages can be templated after the existing DNASC pages such as the ``Plate History'' page. This 
includes functions such as table filters and a search bar. 
% add screenshots as supplementary materials
These modified screenshots of the ``Plate History'' page 
demonstrate how each new page should look.

\section{Aims of this specification}

This spec aims to:

\begin{itemize}
  \item Detail all aspects of the expanded website and its features.
  \item Provide instructions from a high level.
\end{itemize}

\section{References to externally documented terms}

This specification will detail essential data models and logic. A special font will be used to indicate a model 
or function defined in this specification, or endpoints or properties belonging to a Globus API. Links to API 
documentation are also provided.

