% chapter: sharing

\section{Overview}

This chapter will describe the contents of the sharing pop-up window. This pop-up allows 
the user to share the given movie with a Globus user. It also lists Globus users who 
have access to the given movie and gives the website user the opportunity revoke a 
Globus user's access. This pop-up window should be opened by clicking a cell in 
the ``Shares'' column of the movies table.

\section{Content}

The sharing pop-up window should consist of two sections: one containing a listing of
Globus users who have access to the movie and one for sharing the movie with a new
Globus user. 

\subsection{Users with access section}

The users with access section should contain a listing of Globus users who have access 
to the movie. This listing should also provide a way to select a user whose access should 
be revoked. The listing should contain the following elements:

\begin{itemize}\itemsep1pt
    \item The name of the user (only if the user is a registered DNASC user)
    \item The user's Globus ID
    \item The date the user was granted access
    \item A button to revoke access
\end{itemize}

\subsection{Share section}

The share section requires the user to provide a Globus username to share the movie with.
It offers a search feature of DNASC users with Globus usernames.

\subsubsection{DNASC user search bar}

The share section should contain a search bar which allows the user to search the DNASC
database for users by name. The results should only be DNASC users who have Globus
usernames. Selecting a result should populate the Globus username field with the selected
user's Globus username. 

\subsubsection{Globus username field}

The share section should contain a text field to allow the user to enter a Globus
username. The user can edit the field directly, or select a DNASC user from the search 
results, which will populate the field automatically.

\subsubsection{Share movie button}

The share section should contain a button which shares the movie with the Globus user.
The share movie button should be disabled (but visible) until a user is selected.
See appendix \ref{appendix:sharemovie} for implementation details.